%-------------------------%
% Resume in Latex
% Author : Najam
%------------------------%


\documentclass[letterpaper,11pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}




\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}


\urlstyle{same}


\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
     
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}




\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}


\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}




\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Najam Ali Abass} \\ \vspace{1pt}
    House 24 Street 586, G13/2 Islamabad \\ \vspace{1pt}
    \small \href{tel:+92-3173036098}{ \raisebox{-0.1\height}\faPhone\ \underline{+92-3173036098} ~} \href{mailto:najamabass2020@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{najamabass2020@gmail.com}} ~
    \href{https://www.linkedin.com/in/ctoic/}{\raisebox{-0.1\height}\faLinkedinSquare\ \underline{Najam}}  ~
    \href{https://github.com/Ctoic}{\raisebox{-0.2\height}\faGithub\ \underline{ctoic}} ~
    \href{https://www.instagram.com/dev_with_ctoic}{\raisebox{-0.2\height}\faInstagram \underline{ctoic}} ~
    \href{https://codeforces.com/profile/yourid}{\raisebox{-0.2\height}\faYoutube\ \underline{Ishowscience}}
    
    
    \vspace{-8pt}
\end{center}




%-----------EDUCATION-----------
\section{EDUCATION}
 \resumeSubHeadingListStart
    \resumeSubheading
      {FAST-National University Of Computer and Emerging Science}{08 2021 -- Present}
      {Bs Computer Science    }{Islamabad, Pakistan}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {FAST-NUCES,}{08 2020 -- 07 2021}
      {Bs Software Engineering }{Peshawer, Pakistan}
  \resumeSubHeadingListEnd
 
  \resumeSubHeadingListStart
    \resumeSubheading
      {Aga Khan Higher Secondary School, Gilgit}{08 2021 -- Present}
      {HSSC(I \& II)  }{Gilgit Baltistan, Pakistan}
  \resumeSubHeadingListEnd


%------RELEVANT COURSEWORK-------
\section{COURSEWORK / SKILLS}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-3pt, parsep=5pt]
                \item Programming Fundamentals in (C++ and Python)
                \item Data Structures \& Algorithms
                \item Operating Systems
                \item Information Security
                \item Database Management System (DBMS)
                \item Artificial Intelligence
                \item OOPS Concept
                \item Web Development
                \item Image Processing 
                \item Computer Networks
                \item Statistics 
                \item Software Engineering
                \item Theory Of Automata 
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart

    \resumeProjectHeading
    {\href{https://github.com/Ctoic/Hostel-management-System-Project.git}{\textbf{\large{\underline{Hostel Management System}}} \href{https://github.com/Ctoic/Hostel-management-System-Project.git }{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Html,CSS,JavaScript,PHP,SQL,Xamp }}}{04 2024}
    \resumeItemListStart
      \resumeItem{\normalsize{  This Project is web application built with php,javascript , html and css for managing hostels.

      \textbf{highlight key points}.}}
      \resumeItem{\textcolor{accent} {\href{Project Link} {\underline{\normalsize{Download}}}}}
    \resumeItemListEnd
    \vspace{-13pt}

      \resumeProjectHeading
          {\href{https://github.com/Ctoic/Infix-Postfix-Prefix-Converter.git}{\textbf{\large{\underline{Infix to Postfix and Prefix Converter}}} \href{Project Link}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{C++, Data Structures, Stacks, Linked Lists }}}{03 2021}
          \resumeItemListStart
            \resumeItem{\normalsize{This project provides a simple implementation of a stack-based algorithm to convert infix expressions to postfix (Reverse Polish Notation) and prefix (Polish Notation) expressions. It also includes functionality to evaluate postfix expressions.

            \textbf{highlight key points}.}}
            \resumeItem{\textcolor{accent} {\href{Project Link} {\underline{\normalsize{Download}}}}}
          \resumeItemListEnd
          \vspace{-13pt}
         
          \resumeProjectHeading
          {\href{https://github.com/Ctoic/Algorithm-Visualizer-Using-pygame}{\textbf{\large{\underline{Algorithm Visualizer}}} \href{https://github.com/Ctoic/Algorithm-Visualizer-Using-pygame}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Python, Pygame}}}{04 2022}
          \resumeItemListStart
            \resumeItem{\normalsize{In this project we have used python language because of it's extensive librarires and easy syntax. \textbf{Insertion sort
            All Sorting Algorithm implementation} }}
           
          \resumeItemListEnd

          \resumeProjectHeading
          {\href{ProjectLink.com}{\textbf{\large{\underline{Task Manager}}} \href{https://github.com/Ctoic/Task-Manager.git}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Html,CSS,Bootstrap,Javascript,Github,Python, Flask,jinjatemplate2}}}{06 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{ Web Application for tracking your daily tasks using flask. \textbf{Python,Flask,GitHub}.}}

          \resumeItemListEnd
          \vspace{-4pt}

          \resumeProjectHeading
          {\href{https://lisbook.netlify.app/}{\textbf{\large{\underline{Lisbook}}} \href{https://github.com/Ctoic/Lisbook}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Html,CSS,Javascript,Github,Netlify}}}{06 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{ Web application for listening to books. Built with HTML, CSS, and JavaScript. Deployed on Netlify. \textbf{Open-source on GitHub}.}}
            \resumeItem{\normalsize{ Features include: \textbf{audio playback, bookmarking, progress tracking, and a user-friendly interface}.}}
          \resumeItemListEnd
          \vspace{-13pt}
 
    \resumeSubHeadingListEnd
\vspace{-1pt}
%-----------EXPERIENCE-----------
\section{INTERNSHIP}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Github Education \href{https://github.com/Ctoic/CalHub.git}{\raisebox{-0.1\height}\faExternalLink }}{10 2023 -- 11 2023}
      {\underline{Maintainer and Contributer at open source Event}}{Remote, GitHub}
      \resumeItemListStart
        \resumeItem{\normalsize{About the role \textbf{Open Source , Github , Version Control , Web Development}}}
 
      \resumeItemListEnd  

      \resumeSubheading
      {C3 Akademia\href{https://c3akademia.com/}{\raisebox{-0.1\height}\faExternalLink }}{10 2023 -- 11 2023}
      {\underline{Website Developer  }}{Onsite, C3 Akademia}
      \resumeItemListStart
        \resumeItem{\normalsize{Along with my team I created website for C3 Akademia. It is an online tuition academy for CSS Aspirants. We also Wrote technical and non technical blogs to increase visitors on the website. \textbf{Web Development, WordPress,Plugins,PHP,Marketing,Graphic Design}}}
 
      \resumeItemListEnd  

      \resumeSubheading
      {Comprehensive Community Care Hostel }{12 2022 -- Present}
      {\underline{Manager}}{Onsite, Islamabad}
      \resumeItemListStart
        \resumeItem{\normalsize{As a manager I have to supervise 35 student and 3 employee. We conduct seminars and workshops realted to latest technology.\textbf{Management,Communication,Community,Leadership}}}
 
      \resumeItemListEnd  

  \resumeSubHeadingListEnd
\vspace{-12pt}
%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{ \normalsize{Python, Java, C, C++, JavaScript, SQL, R}} \\
     \textbf{\normalsize{Developer Tools:}}{ \normalsize{VS Code, Android Studio, Intellij Idea Ultimate, Visual Studio,Beekeper Studio,Blender,Figma,Canva,Linux}} \\
     \textbf{\normalsize{Technologies/Frameworks:}}{\normalsize{ Linux, GitHub, ReactJS, Bootstrap,Streamlit,WordPress, Git, Mongo,Gradio,.net ,Netlify}} \\
    }}
 \end{itemize}
 \vspace{-15pt}


%-----------INVOLVEMENT---------------
\section{Achievements}
\resumeSubHeadingListStart
    \resumeSubheading{Dean's List   }{Bs Software Engineering}{\underline{}}{Fast-Nuces,Peshawer}
        \resumeItemListStart
            \resumeItem{\normalsize{For Securing a GPA over 3.5/4 in fall 2020. I was added in the Dean's List.}}
        \resumeItemListEnd

      
        \resumeSubheading{Bronze Medal }{Bs Software Engineering}{\underline{}}{Fast-NUCES, Peshawer}
        \resumeItemListStart
            \resumeItem{\normalsize{I got third position in my department for the fall semester 2020.}}
        \resumeItemListEnd

        
\resumeSubHeadingListEnd
\vspace{-11pt} 


%-----------INVOLVEMENT---------------
\section{EXTRACURRICULAR}
    \resumeSubHeadingListStart
        \resumeSubheading{Ismaili Boy Scout Association  }{02 2007 -- Present}{\underline{Head Media}}{Gilgit Baltistan}
            \resumeItemListStart
                \resumeItem{\normalsize{Helping community in need and teaching the young generation to equip their self with the latest technology. I was eager to contribute to my community from a young age, I was 7 when I joined the organization as a Shaheen Scout then I become a Boyscout finally I headed the scout in 2015. But then I have to move to city for education I left my position but I always conduct online meeting and drives to help the community.}}
                \resumeItem{\normalsize{Participation Certificate. \href{ParticipationCertificateLink.com}{\raisebox{-0.1\height}\faExternalLink }}}
            \resumeItemListEnd

          
            \resumeSubheading{Fast Developer Club }{11 2021 -- 04 2023}{\underline{Web Developer}}{Fast-NUCES, Islamabad}
            \resumeItemListStart
                \resumeItem{\normalsize{Workshops on Github and Web development for the juniors at university campus. Organized Web dev competitions at University Biggest Event.}}
            \resumeItemListEnd

            \resumeSubheading{NASCON }{02 2023 -- 06 2023}{\underline{Event Organizer}}{Fast Islamabad}
            \resumeItemListStart
                \resumeItem{\normalsize{Coordinated events and activities for NASCON, focusing on technoWeb logy and innovation.}}
            \resumeItemListEnd


            \resumeSubheading{Head Boy }{02 2018 -- 04 2020}{\underline{Head Boy}}{Aga Khan Higher Secondry School Gilgit}
            \resumeItemListStart
                \resumeItem{\normalsize{Led student council initiatives and represented the student body in various functions.}}
            \resumeItemListEnd
            
    \resumeSubHeadingListEnd
 \vspace{-11pt} 
 \section{HOBBIES}
\resumeSubHeadingListStart
\resumeSubheading{}{}{}{}
\resumeItemListStart
\resumeItem{\normalsize{Reading and watching science fiction books and movies.}}
\resumeItem{\normalsize{Playing football and working out at the gym.}}
\resumeItem{\normalsize{Gardening and growing a variety of plants.}}
\resumeItem{\normalsize{Mountaineering and exploring new heights.}}
\resumeItem{\normalsize{Swimming and improving aquatic skills.}}
\resumeItem{\normalsize{Storytelling and engaging audiences with creative tales.}}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}





